Type Error Telemetry at Scale

### 2023-09-24 programming23/paper.tex
quick sec 5 notes

A close inspection of the data revealed a few anomalies.
For the most part, we omit the strange data from futher
analysis.\todo{I'm inclined to rewrite this to be much more concise.}

@@

\begin{figure}[t]
  %% strict
  %%  te total 22771
  %%  mean 6.9 std 26.24592591869705 med 1 max 385
  %% 
  %%  fs total 114259
  %%  mean 34.9 std 155.41955823164017 med 1 max 4789
  %% 
  %% nonstrict
  %%  te total 362964
  %%  mean 2.3 std 66.44456626891912 med 0 max 13511
  %% 
  %%  fs total 7546175
  %%  mean 48.6 std 270.60578740369266 med 3 max 16712

@@

@@

All three counts are imprecise because our telemetry does not track the exact
identity of a type error.
Suppose a creator removes one \code{CannotCallNonFunction} error but then
immediately introduces another on a different line.
\Cref{t:type-error-survival} reports this pair of edits as a Keep rather than
an Add and a Remove because we cannot distinguish two errors of the same kind.

@@

@@

TODO nocheck accumulated fs errors?

@@

>>>>

A close inspection of the data revealed a few anomalies.
For the most part, we omit the strange data from futher
analysis.\todo{I'm inclined to rewrite this to be much more concise.}\todo{agreed}

@@

\begin{figure}[t]
  %% strict
  %%  te total 22771
  %%  mean 6.9 std 26.24592591869705 med 1 max 385
  %% 
  %%  fs total 114259
  %%  mean 34.9 std 155.41955823164017 med 1 max 4789
  %% 
  %% nonstrict
  %%  te total 362964
  %%  mean 2.3 std 66.44456626891912 med 0 max 13511
  %% 
  %%  fs total 7546175
  %%  mean 48.6 std 270.60578740369266 med 3 max 16712
  %%
  %% nocheck
  %%  te total 176309
  %%  mean 0.13 std 1.9040337635815197 med 0 max 289
  %% 
  %%  fs total 63784284
  %%  mean 47.7 std 885.8225471699477 med 1 max 251131

@@

\FILL{} average number of FS errors is
worst in \mnonstrict{}, 49, vs 48 nocheck and 7 strict.
median is 3 NS, 1 nocheck, 1 strict.
We might optimistically think that nocheck accumulates
lots of errors, but no that does not seem to be the case,
NS and nocheck both apparently fine with latent FS errors.

@@

All three counts are imprecise because our telemetry does not track the exact
identity of a type error.
Suppose a creator removes one \code{CannotCallNonFunction} error but then
immediately introduces another on a different line.
\FILL{} beware, don't say this same thing Nx throughout the paper.
\Cref{t:type-error-survival} reports this pair of edits as a Keep rather than
an Add and a Remove because we cannot distinguish two errors of the same kind.

@@

... very concerning if this is the top takeaway

\paragraph{Good: No Apparent Turmoil With Upgrades / Downgrades}

But, mode switches are very rare!
Really too soon to draw any conclusion, this is only a lack of bad.

@@

TODO nocheck accumulated fs errors?
Need this (density fs) to say more about whether errors get fixed,
same goes for fig 10.

\paragraph{... Something About Add/Drop in Edit Range}

\paragraph{Bad: Strict too Strict}

Comparing NS vs S, the syntax error \% is about the same (15 vs 9)
but the type mismatch \% is far off (2 vs 20).
S is probably noisy.

Data model is probably part of this.

@@

\paragraph{Big Bad: Low Adoption}

poor advertising,
unclear value proposition,
nocheck code is apparently doing fine despite lots of forced strict errors,
... can we say this outright?!
